How Slow do my Transient Typechecks Go?

### 2019-08-17 paper.tex
Make new/old copyedits in S5

\section{Individual Annotations}
\label{s-individual}
\begin{figure*}
        \input{graphs/pattern}
        \caption{Pairs of colour-coded scatter and column graphs. The scatter graphs represent the performance of a sample of typing lattice. The column graphs show the performance of every configuration with only one type annotation. The scatter plots and column graphs are colour-coded based on whether a particular type annotation or two are present in the source code.}
        \label{f:pattern}              
\end{figure*}
We hypothesise that the bi/tri-modal graphs shown in figure~\ref{f:full} are caused by a few, highly significant type annotations: i.e.\ there are a very few annotaitons that determine each benchmark's performance.

@@

As an alternative, less labour intensive approach to identifying
potentially influential type annotations, we measured one additional
configuration for each type annotation in each benchmark, with only
that single type annotation present. Our aim was to compare the overhead of
each type annotation in isolation against the baseline without any
type checks.

@@

This figure shows a pair of graphs for a selection of ten benchmarks: a scatterplot and a column graph.  \kjx{are they actualy histograpms? or just bar charts?}\mwh{It's a column graph, like Isaac said - histograms have a continuous axis and bar charts are spaced.}
\kjx{argh. should figure do histograph first then scatterplot?}
The column graphs show the execution times of each configurations for each individual annotation in a benchmark. The x-axis of the graphs indicates the index of this annotation in the order they appear in the source code. The first column represents the 1\textsubscript{st} annotation, and the last column represents the last one. The y-axes for the column graphs are the same as the associated scatter graph, showing the execution time of each configuration.\footnote{Although the right y-axes for the column graphs appear to be identical the scatter plot axes, they are relative to performance results collected on different days: this was to ensure that the performance of the test computer had not changed significantly from when the typing lattice experiments were run.}\kjx{do we need the footnote?}

@@

As can be seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmark, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing lattice graphs. For Permute there is actually a signficant performance \emph{increase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight increase in performance, but here this is caused by two type annotations (in red and blue), but this does not appear to be cumulative: the purple dots are about the same height as the red and blue ones, so \textit{either} annotation is sufficient for the full benefit.

>>>>

\section{Individual Annotations}
\label{s-individual}
\begin{figure*}
        \input{graphs/pattern}
        \caption{Pairs of colour-coded scatter and column graphs. The scatter graphs represent the performance of a sample of typing lattice. The column graphs show the performance of every configuration with only one type annotation. The scatter plots and column graphs are colour-coded based on whether a particular type annotation or two are present in the source code.}
        \label{f:pattern}              
\end{figure*}
We hypothesise that the bi/tri-modal graphs shown in figure~\ref{f:full} are caused by a few, highly significant type annotations: i.e.\ there are a very few annotations that determine each benchmark's performance.

@@

As an alternative, less labour intensive approach to identifying
potentially influential type annotations, we measured one additional
configuration for each type annotation in each benchmark, with only
that single type annotation present. Our aim was to compare the overhead of
each type annotation in isolation against the no-typecheck baseline.

@@

This figure shows a pair of graphs for a selection of ten benchmarks: a scatterplot and a column graph.  \kjx{are they actualy histograpms? or just bar charts?}\mwh{It's a column graph, like Isaac said - histograms have a continuous axis and bar charts are spaced.}
\kjx{argh. should figure do histograph first then scatterplot?}
The column graphs show the execution times of each configurations for each individual annotation in a benchmark. The x-axis of the graphs indicates the index of this annotation in the order they appear in the source code. The first column represents the 1\textsubscript{st} annotation, and the last column represents the last one. The y-axes for the column graphs are the same as the associated scatter graph, showing the execution time of each configuration.\footnote{Although the right y-axes for the column graphs appear to be identical to the scatter plot axes, they are relative to performance results collected on different days: this was to ensure that the performance of the test computer had not changed significantly from when the typing lattice experiments were run.}\kjx{do we need the footnote?}

@@

As can be seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmarks, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing lattice graphs. For Permute there is actually a signficant performance \emph{increase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight increase in performance, but here this is caused by two type annotations (in red and blue); this effect does not appear to be cumulative, however: the purple dots are about the same height as the red and blue ones, so \textit{either} annotation is sufficient for the full benefit.
